Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-12 Draft/Draft.Rmd
Edits

In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs (more densenly connected) in contrast to core-peripheral motifs (less densenly connected) that were under-represented. As expected, the functional group of bees (the one with the highest number of interactions) was the most abundant in the different network motif positions. This is likely to be the case for most plant-pollinator systems as bees are generally the main functional group visiting flowers in plant-pollinator communities [@ollerton2017]. Interestingly, bees were highly over-represented in fan motif positions 4, 16 and 46 (**Figure 3**) which are associated with the highest levels of generalism. Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles between mirror image motifs in fan positions that involve pollinator specialization and generalism). Despite this in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs. Further, unlike floral visitors, plant functional groups showed little differences across them on the different motif positions. However, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], also showed high over-representation on the same fan motif that bees did but for the plant positions (**Figure 3**).

3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.

4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …

@@

- Paper of Poisot 2020

5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.

>>>>

In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs (more densenly connected) in contrast to core-peripheral motifs (less densenly connected) that were under-represented. As expected, the functional group of bees (the one with the highest number of interactions) was the most abundant in the different network motif positions. This is likely to be the case for most plant-pollinator systems as bees are generally the main functional group visiting flowers in plant-pollinator communities [@ollerton2017]. Interestingly, bees were highly over-represented in fan motif positions 4, 16 and 46 (**Figure 3**) which are associated with the highest levels of generalism. Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles between mirror image motifs in fan positions that involve pollinator specialization and generalism). Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs. Unlike floral visitors, plant functional groups showed little differences across them on the different motif positions. However, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], also showed high over-representation on the same fan motif that bees did (**Figure 3**).

The observed functional group probabilities on the different positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existance of ecological processes shaping their structure. In addition, we found that just 30% of the observed motif combinations took place. This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016]. Thus, similarly to the presence of forbidden links, we found the existence of forbidden motifs.

---
THIS IS A COMMENT
3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.
---

Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems.

---
THIS IS ACOMMENT
4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …

Although functional groups can define

@@

- Paper of Poisot 2020
---

---
THIS IS A COMMENT
5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
---
